### 2020-06-30 paper/preprint/paper_revised_submission_june2020_apa.Rmd
code for rendering preprint

---
title:  |
  | Detecting social information in a dense database
  | of infants’ natural visual experience
bibliography: library.bib
csl: apa6.csl
document-params: "10pt, letterpaper"

author-information: >

abstract: >
        The faces and hands of caregivers and other social partners offer a rich source of social and causal information that may be critical for infants' cognitive and linguistic development. Previous work using manual annotation strategies and cross-sectional data has found systematic changes in the proportion of faces and hands in the egocentric perspective of young infants. Here, we examine the prevalence of faces and hands in a longitudinal collection of nearly 1700 headcam videos collected from three children along a span of 6 to 32 months of age—the SAYCam dataset [@SAYcam]. To analyze these naturalistic infant egocentric videos, we first validated the use of a modern convolutional neural network of pose detection (OpenPose) for the detection of faces and hands. We then applied this model to the entire dataset, and found a higher proportion of hands in view than previous reported and a moderate decrease the proportion of faces in children's view across age. In addition, we found variability in the proportion of faces/hands viewed by different children in different locations (e.g., living room vs. kitchen), suggesting that individual activity contexts may shape the social information that infants experience.

keywords: >
    social cognition; face perception; infancy; head cameras; deep learning

output: cogsci2016::cogsci_paper
#final-submission: \cogscifinalcopy
---
\newcommand{\wrapmf}[1]{#1}

@@

```{r, libraries}
library(png)
library(grid)
library(ggplot2)
library(xtable)
library(knitr)
library(tidyverse)
library(assertthat)
library(ggthemes)
library(lme4)
library(langcog)
library(lsr) 
library(stringr)
library(lmerTest)

theme_set(theme_few())
# renv::init()
# https://rstudio.github.io/renv/articles/renv.html
```

@@

```{r}
## Read in data 
### Load preprocessed and filtered detections
load('../../data_cogsci/openpose_detections_filtered_2020-01-29.RData') # d_all
load('../../data_cogsci/openpose_detections_filtered_cropped_2020-01-29.RData') # d_cropped
```

```{r}
### Choose bins across which to analyze data
bin_size = 7 # days
min_age = min(d_all$age_days)
max_age = max(d_all$age_days)
bin_starts = seq(min_age-1, max_age+1,bin_size)
bins = c(bin_starts, max_age)
```

```{r} 
### How large is the dataset we're analyzing?
num_frames = length(d_all$frame)

fps=30
num_seconds = length(d_all$frame)/fps
num_videos = length(unique(d_all$vid_name))
num_minutes = num_seconds/60
num_hours = num_minutes/60
num_days = num_hours/24 
```

@@

 ## load gold sample annotations
 load('../../data_cogsci/gold_sample_annotations2020-01-31.RData') # gold_sample, pre-filtered

 ## evaluate detectors
 gold_sample <- gold_sample %>%
  mutate(face_eval_ketan = evaluate_detector(face_present_ketan, face_openpose), hand_eval_ketan = evaluate_detector(hand_present_ketan, hand_openpose))

@@

```{r}
### Examine gold sample performance by child hands
load('../../data_cogsci/child_adult_hand_annotations_by_frame.RData')
# 
hands_missed <- gold_sample %>%
  left_join(child_adult_hand_annotations, by=(c("vid_name","frame"))) %>%
  filter(!is.na(full_image_path)) %>%
  filter(hand_eval_ketan == 'FN')

gold_sample_no_child_hands <- gold_sample %>%
  left_join(child_adult_hand_annotations, by=(c("vid_name","frame"))) %>%
  replace_na(list(child_hand_seg = FALSE)) %>% # replace NAs with false (frames not in annotations (NAs) did not have hands) 
  filter(child_hand_seg==FALSE) %>% # now these are counted as frames where OP didn't need to detect something
  mutate(hand_eval_adults = evaluate_detector(hand_present_ketan, hand_openpose))

@@

```{r} 
### Load turk hand annotations with all bounding boxes (multiple dets per frame)
load("../../data_cogsci/hand_annotations_2020-01-29.RData")

@@

```{r}
vid_info <- d_all %>%
  select(vid_name, frame, age_days, child_id)

## summary stats for gold sample detections
summary_by_age_gold <- gold_sample %>%
  left_join(vid_info) %>%
  mutate(age_day_bin = cut(age_days, bins, labels=round(bin_starts/30,1))) %>%
  mutate(age_day_bin = as.numeric(as.character(age_day_bin))) %>%
  group_by(age_day_bin, child_id) %>%
  summarize(num_detect = length(face_present_ketan), prop_faces = sum(face_present_ketan) / num_detect,  prop_hands = sum(hand_present_ketan) / num_detect)

## Make summary stats for cropped and uncropped detedctions
summary_by_age <- d_all %>%
  mutate(age_day_bin = cut(age_days, bins, labels=round(bin_starts/30,1))) %>%
  mutate(age_day_bin = as.numeric(as.character(age_day_bin))) %>%
  group_by(age_day_bin, child_id) %>%
  summarize(num_detect = length(face_openpose), prop_faces = sum(face_openpose) / num_detect,  prop_hands = sum(hand_openpose) / num_detect)

summary_by_age_cropped <- d_cropped %>%
  replace_na(list(hand_detected = FALSE, face_detected = FALSE)) %>%
  mutate(age_day_bin = cut(age_days, bins, labels=round(bin_starts/30,1))) %>%
  mutate(age_day_bin = as.numeric(as.character(age_day_bin))) %>%
  group_by(age_day_bin,child_id) %>%
  summarize(num_detect = length(face_openpose), prop_faces = sum(face_detected) / num_detect,  prop_hands = sum(hand_detected) / num_detect)

##
wide_gold <- summary_by_age_gold %>%
  gather(region, prop, prop_faces, prop_hands) %>%
  mutate(approach = "gold", region = ifelse(region == "prop_faces","Face","Hands"))  %>%
  filter(!is.na(child_id)) # weird video

wide_cropped <- summary_by_age_cropped %>%
  gather(region, prop, prop_faces, prop_hands) %>%
  mutate(approach = "cropped",
         region = ifelse(region == "prop_faces","Face","Hands"))  %>%
  filter(num_detect > 5000) # eliminate one data point that skews scaling

wide_uncropped <- summary_by_age %>%
  gather(region, prop, prop_faces, prop_hands) %>%
  mutate(approach = "uncropped",
         region = ifelse(region == "prop_faces","Face","Hands"))  %>%
  filter(num_detect > 5000) # eliminate one data point that skews scaling

@@

```{r FacesAndHands, fig.env="figure*", fig.pos = "h", fig.align = "center", fig.width=7, fig.height=3, fig.cap = "Proportion of faces and hands seen as a function of age for each child in the dataset. Data are binned by each week that the videos were filmed and scaled by the number of frames in that age range. Dashed lines show estimated trend lines from proportion of faces/hands in view when detections are restricted to the upper 60 percent of the FOV, reducing the contribution of children's own hands; dotted lines show estimated trend lines for human annotations on the 24K gold set."}

ggplot(wide_uncropped, 
       aes(x=age_day_bin, y=prop, 
           size=log10(num_detect),
           col=region)) +
  geom_point(alpha=.2) +
  geom_smooth(span=10, aes(weight = num_detect), show.legend = FALSE) + # geom_smooth(show.legend = FALSE) or move these below legend?
  geom_smooth(data = wide_cropped, aes(weight = num_detect), show.legend = FALSE, 
              lty = 2, span=10, se = FALSE) +
  geom_smooth(data = wide_gold, aes(weight = num_detect), show.legend = FALSE,
              lty = 3, span=10, se = FALSE) +
  ylab('Proportion Detections') + 
  xlab('Age (Months)') +
  ylim(0,.5) +
  facet_grid(.~child_id) + 
  theme_few(base_size=9) +
  ggthemes::scale_color_solarized(name = "") + 
  scale_size_continuous(name = "Detections (Log 10)") +
  theme(legend.text=element_text(size=8)) +
  theme(legend.position="bottom")

@@

We analyzed the social information in view across the entire dataset, looking specifically at the proportions of faces and hands that were in view for each child.^[All analyses and preprocessed data files for this paper are avaliable at https://tinyurl.com/detecting-social-info] Data from videos were binned according to the age of the child (in weeks). First, we saw that the proportion of faces in view showed a moderate decrease across this age range (see Figure \ref{fig:FacesAndHands}); in contrast, we did not observe an increase in the proportion of hands in view, but rather a slight decrease. These effects were quantified with two separate linear mixed-models (see Tables 1 & 2).^[Face/hand detections were binned across each week of filming. Participant's age was converted into months and centered for these analyses. Random slopes for the effect of age by child led to a singular fit and were removed from both analyses; see full model specification in accompanying codebase.]

```{r}
# replace NAs with FALSE to compare proportion hands detected
d_cropped <- d_cropped %>%
  replace_na(list(hand_detected = FALSE, face_detected = FALSE))
```

As children's hands tended to occur in the lower visual field (see Figure \ref{fig:handLocation}), we thus re-analyzed the entire dataset while restricting our analysis to the upper 60% of the field of view, decreasing the proportion of hand detections from `r round(mean(d_all$hand_openpose),2)*100`% to `r round(mean(d_cropped$hand_detected),2)*100`%, but only decreased face detections from `r round(mean(d_all$face_openpose),2)*100`% to `r round(mean(d_cropped$face_detected),3)*100`%. This cropping likely removed both the majority of detections of children's own hands but also some detections of adult hands (see Figure \ref{fig:handLocation}), especially as OpenPose was biased to miss children's hands when they were in view. Nonetheless, within this modified field of view, we still observed more hand detections than face detections (see dashed lines in Figure \ref{fig:FacesAndHands}).

```{r eval=FALSE}
summary_by_age_days_cropped <- d_cropped %>%
  replace_na(list(hand_detected = FALSE, face_detected = FALSE)) %>%
  group_by(age_days,child_id) %>%
  summarize(num_faces = sum(face_openpose), num_hands = sum(hand_detected), num_detect = length(face_openpose)) %>%
  mutate(prop_faces = num_faces / num_detect, prop_hands = num_hands / num_detect) 
summary_by_age_days_cropped$age_scale <- scale(summary_by_age_days_cropped$age_days, scale = FALSE)[,1] / 30.3

summary_by_age_days <- d_all %>%
  group_by(age_days,child_id) %>%
  summarize(num_faces = sum(face_openpose), num_hands = sum(hand_openpose), num_detect = length(face_openpose)) %>%
  mutate(prop_faces = num_faces / num_detect, prop_hands = num_hands / num_detect) 
summary_by_age_days$age_scale <- scale(summary_by_age_days$age_days, scale = FALSE)[,1] / 30.3

```{r eval=FALSE}
# run lmer models -- faces over age
faces_model_full_age_out = summary(lmer(prop_faces ~ age_scale + (1 | child_id), data = summary_by_age_days_cropped))

# hands over age
hands_model_full_age_out = summary(lmer(prop_hands ~ age_scale + (1 | child_id), data = summary_by_age_days_cropped))

# explicit modeling of faces vs. hands and interaction with age
# main effect of ages and regions; no interaction.
wide_cropped_age_days <- summary_by_age_days_cropped %>%
  gather(region, prop, prop_faces, prop_hands) %>%
  mutate(approach = "cropped",
         region = ifelse(region == "prop_faces","Face","Hands"))

diff_model_full_age_out = summary(lmer(prop ~ region*age_scale + (1 | child_id), data = wide_cropped_age_days))
```

```{r eval=FALSE}
xtable(faces_model_full_age_out$coefficients, digits=c(4,3,3,3,3,3),"Model coefficients from a linear mixed model predicting the proportion of faces seen by infants.")

xtable(hands_model_full_age_out$coefficients, digits=c(4,3,3,3,3,3),"Model coefficients from a linear mixed model predicting the proportion of hands seen by infants.")
```

\begin{table}[ht]
\centering
\begin{tabular}{rrrrrr}
  \hline
 & Estimate & Std. Err. & df & t value & Pr($>$$|$t$|$) \\ 
  \hline
(Int.) & 0.179 & 0.008 & 2.180 & 22.736 & 0.001 \\ 
  Age & -0.002 & 0.001 & 402.024 & -3.138 & 0.002 \\ 
   \hline
\end{tabular}
\caption{Model coefficients from a linear mixed model predicting the proportion of faces seen by infants.} 
\end{table}

\begin{table}[ht]
\centering
\begin{tabular}{rrrrrr}
  \hline
 & Estimate & Std. Error & df & t value & Pr($>$$|$t$|$) \\ 
  \hline
(Int.) & 0.238 & 0.011 & 1.913 & 22.359 & 0.002 \\ 
  Age & -0.002 & 0.001 & 409.966 & -2.286 & 0.023 \\ 
   \hline
\end{tabular}
\caption{Model coefficients from a linear mixed model predicting the proportion of hands seen by infants.} 
\end{table}

## Access to social information in different locations
```{r}
load('../../data_cogsci/saycam_metadata.RData') # meta

@@

```{r}
d_by_location_cropped <- d_cropped %>%
  replace_na(list(hand_detected = FALSE, face_detected = FALSE)) %>%
  mutate(age_day_bin = cut(age_days, bins, labels=round(bin_starts/30,1))) %>%
  mutate(age_day_bin = as.numeric(as.character(age_day_bin))) %>%
  left_join(meta) %>%
  filter(!is.na(Location)) %>%
  filter(count_locations==1) 
# 
d_by_location_cropped$Location = droplevels(d_by_location_cropped$Location) # get rid of unused levels (more than 1 location)
# merge locations that seem similar
levels_to_modify = levels(d_by_location_cropped$Location)
levels_to_modify[10] = 'Outside' # Outside on property
levels_to_modify[12] = 'Outside' # Off Property
# reset levels for both cropped/uncropped
levels(d_by_location_cropped$Location) <- levels_to_modify

face_hand_by_location_cropped <- d_by_location_cropped %>%
  group_by(Location,child_id,age_day_bin) %>%
  summarize(prop_faces = mean(face_openpose), prop_hands = mean(hand_openpose), prop_hands_cropped = mean(hand_detected), num_detect = length(hand_detected))  %>%
  group_by(Location) %>%
  filter(num_detect > 12000)  ##

## Compute CIs for faces/hands by each location, and then merge back raw data so they can be plotted together
## Get rid of any locations where we didn't have enough data to make a CI (not more than 1 age_bin)
hands_to_plot_cropped <- face_hand_by_location_cropped %>%
  group_by(Location, child_id) %>%
  multi_boot_standard(col="prop_hands_cropped") %>%
  mutate(region = "Hands (Cropped)") %>%
  ungroup %>%
  left_join(face_hand_by_location_cropped) %>%
  mutate(prop = prop_hands_cropped) %>%
  select(-prop_faces, -prop_hands, -prop_hands_cropped) %>%
  filter(!is.na(ci_lower))

hands_to_plot <- face_hand_by_location_cropped %>%
  group_by(Location, child_id) %>%
  multi_boot_standard(col="prop_hands") %>%
  mutate(region = "Hands") %>%
  ungroup %>%
  left_join(face_hand_by_location_cropped) %>%
  mutate(prop = prop_hands) %>%
  select(-prop_faces, -prop_hands, -prop_hands_cropped) %>%
  filter(!is.na(ci_lower))

faces_to_plot_cropped <- face_hand_by_location_cropped %>%
  group_by(Location, child_id) %>%
  multi_boot_standard(col="prop_faces") %>%
  mutate(region = "Face") %>%
  ungroup %>%
  left_join(face_hand_by_location_cropped) %>%
  mutate(prop = prop_faces) %>%
  select(-prop_faces, -prop_hands, -prop_hands_cropped) %>%
  filter(!is.na(ci_lower))  # if we didn't have enough points to make a CI, filter

all_to_plot <- faces_to_plot_cropped %>%
  full_join(hands_to_plot_cropped) %>%
  full_join(hands_to_plot) %>%
  group_by(Location) %>%
  mutate(num_detect_location = sum(num_detect)) %>%
  ungroup() %>%
  mutate(Location = fct_reorder(Location, num_detect_location))
```

```{r}
### Chi-squared tests for location variability
d_by_location_cropped_mini_S <- d_by_location_cropped %>%
  group_by(Location) %>%
  mutate(num_detect = length(hand_detected))  %>%
  filter(num_detect > 0)  %>%
  filter(child_id == "S") %>%
  select(Location, face_openpose,hand_detected) # using cropped hands here

d_by_location_cropped_mini_A <- d_by_location_cropped %>%
  group_by(Location) %>%
  mutate(num_detect = length(hand_detected))  %>%
  filter(num_detect > 0)  %>% #
  filter(child_id == "A") %>%
  select(Location, face_openpose, hand_detected)

## drop levels
d_by_location_cropped_mini_S$Location = droplevels(d_by_location_cropped_mini_S$Location)
d_by_location_cropped_mini_A$Location = droplevels(d_by_location_cropped_mini_A$Location)

## make smaller dataframes for just faces/hands
d_by_location_cropped_mini_S_face <- d_by_location_cropped_mini_S %>%
  select(Location, face_openpose)

d_by_location_cropped_mini_S_hand <- d_by_location_cropped_mini_S %>%
  select(Location, hand_detected)

d_by_location_cropped_mini_A_face <- d_by_location_cropped_mini_A %>%
  select(Location, face_openpose)

d_by_location_cropped_mini_A_hand <- d_by_location_cropped_mini_A %>%
  select(Location, hand_detected)

# output (runs chi-squared tests in summary)
faces_S_loc = summary(table(d_by_location_cropped_mini_S_face))
hands_S_loc = summary(table(d_by_location_cropped_mini_S_hand))
faces_A_loc = summary(table(d_by_location_cropped_mini_A_face))
hands_A_loc = summary(table(d_by_location_cropped_mini_A_hand))

# effect size estimates
# cramersV(table(d_by_location_cropped_mini_S_face))
# cramersV(table(d_by_location_cropped_mini_S_hand))
# cramersV(table(d_by_location_cropped_mini_A_face))
# cramersV(table(d_by_location_cropped_mini_A_hand))

@@

@@

>>>>

---
title             : "Detecting social information in a dense database of infants’ natural visual experience"
shorttitle        : "Detecting social information"

author: 
  - name          : "Bria L. Long"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "450 Serra Mall, Stanford CA 94305"
    email         : "bria@stanford.edu"
  - name          : "George Kachergis"
    affiliation   : "1"
  - name          : "Ketan Agrawal"
    affiliation   : "1"
  - name          : "Michael C. Frank"
    affiliation   : "1"

affiliation:
  - id            : "1"
    institution   : "Department of Psychology, Stanford University"

# authornote: |
#   Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.
# 
#   Enter author note here.

abstract: |
          The faces and hands of caregivers and other social partners offer a rich source of social and causal information that may be critical for infants' cognitive and linguistic development. Previous work using manual annotation strategies and cross-sectional data has found systematic changes in the proportion of faces and hands in the egocentric perspective of young infants. Here, we examine the prevalence of faces and hands in a longitudinal collection of nearly 1700 headcam videos collected from three children along a span of 6 to 32 months of age—the SAYCam dataset [@SAYcam]. To analyze these naturalistic infant egocentric videos, we first validated the use of a modern convolutional neural network of pose detection (OpenPose) for the detection of faces and hands. We then applied this model to the entire dataset, and found a higher proportion of hands in view than previous reported and a moderate decrease the proportion of faces in children's view across age. In addition, we found variability in the proportion of faces/hands viewed by different children in different locations (e.g., living room vs. kitchen), suggesting that individual activity contexts may shape the social information that infants experience.

keywords          : "social cognition; face perception; infancy; head cameras; deep learning"
wordcount         : "3444"

bibliography      : ["library.bib"]

floatsintext      : no
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no

documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_pdf
---

```{r setup, include = FALSE}
library("papaja")
```

@@

```{r, libraries}
library(png)
library(grid)
library(ggplot2)
library(xtable)
library(knitr)
library(tidyverse)
library(assertthat)
library(ggthemes)
library(lme4)
library(langcog)
library(lsr) 
library(stringr)
library(lmerTest)
library(here)
theme_set(theme_few())
```

@@

```{r}
## Read in data 
load(here::here('data/data_preprint/all_vid_data_from_bbs_june2020.RData')) # all detections
load(here::here('data/data_preprint/all_centered_vid_data_from_bbs_june2020.RData')) # centered cropped
```

```{r}
load(here::here('data/data_preprint/gold_sample_from_bbs_june2020.RData')) # gold sample detections
load(here::here('data/data_preprint/gold_sample_annotations2020-01-31.RData')) # human annotations
```

```{r} 
### How large is the dataset we're analyzing?
num_frames = sum(all_vid_data$num_detect)

fps=30
num_seconds = sum(all_vid_data$num_detect)/fps
num_videos = length(unique(all_vid_data$vid_name))
num_minutes = num_seconds/60
num_hours = num_minutes/60
num_days = num_hours/24

bin_size = 7 # days
min_age = min(all_vid_data$age_days, na.rm=TRUE)
max_age = max(all_vid_data$age_days, na.rm=TRUE)
bin_starts = seq(min_age-1, max_age+1,bin_size)
bins = c(bin_starts, max_age)
```

@@

#

# join human and OP detections
gold_sample <- gold_sample %>%
  select(vid_name, frame, face_present_ketan, hand_present_ketan) %>%
  mutate(face_present_ketan = as.logical(face_present_ketan), hand_present_ketan = as.logical(hand_present_ketan)) %>%
  right_join(all_gold_sample_frames_op) %>%
  mutate(face_eval_ketan = evaluate_detector(face_present_ketan, face_detected), hand_eval_ketan = evaluate_detector(hand_present_ketan, hand_detected))

@@

```{r}
### Examine gold sample performance by child hands
load(here::here('data/data_preprint/child_adult_hand_annotations_by_frame.RData'))
# 
hands_missed <- gold_sample %>%
  left_join(child_adult_hand_annotations, by=(c("vid_name","frame"))) %>%
  filter(!is.na(full_image_path)) %>%
  filter(hand_eval_ketan == 'FN')

gold_sample_no_child_hands <- gold_sample %>%
  left_join(child_adult_hand_annotations, by=(c("vid_name","frame"))) %>%
  replace_na(list(child_hand_seg = FALSE)) %>% # replace NAs with false (frames not in annotations (NAs) did not have hands) 
  filter(child_hand_seg==FALSE) %>% # now these are counted as frames where OP didn't need to detect something
  mutate(hand_eval_adults = evaluate_detector(hand_present_ketan, hand_detected))

@@

```{r} 
### Load turk hand annotations with all bounding boxes (multiple dets per frame)
load(here::here('data/data_preprint/hand_annotations_2020-01-29.RData'))

@@

```{r}
## summary for all detections
summary_by_age <- all_vid_data %>%
  filter(!is.na(age_days)) %>%
  mutate(age_day_bin = cut(age_days, bins, labels=round(bin_starts/30,1))) %>%
  mutate(age_day_bin = as.numeric(as.character(age_day_bin))) %>%
  group_by(age_day_bin, child_id) %>%
  summarize(num_frames_total = sum(num_detect), num_faces = sum(num_faces), num_hands = sum(num_hands), prop_faces_summary = num_faces / num_frames_total, prop_hands_summary = num_hands / num_frames_total)
```

```{r}
## summary for centered detections
summary_by_age_center <- all_vid_data_center %>%
  filter(!is.na(age_days)) %>%
  mutate(age_day_bin = cut(age_days, bins, labels=round(bin_starts/30,1))) %>%
  mutate(age_day_bin = as.numeric(as.character(age_day_bin))) %>%
  group_by(age_day_bin, child_id) %>%
  summarize(num_frames_total = sum(num_frames), num_faces = sum(num_faces), num_hands = sum(num_hands), prop_faces_summary = num_faces / num_frames_total, prop_hands_summary = num_hands / num_frames_total)
```

```{R}
#### Make wide format for plotting
wide_uncropped <- summary_by_age %>%
  gather(region, prop, prop_faces_summary, prop_hands_summary) %>%
  mutate(approach = "uncropped",
         region = ifelse(region == "prop_faces_summary","Face","Hands"))  %>%
  filter(num_frames_total > 5000) # eliminate small data point that skews scaling

wide_center <- summary_by_age_center %>%
  gather(region, prop, prop_faces_summary, prop_hands_summary) %>%
  mutate(approach = "centered",
         region = ifelse(region == "prop_faces_summary","Face","Hands"))  %>%
  filter(num_frames_total > 5000) # eliminate small data point that skews scaling 
```

```{r FacesAndHands, fig.env="figure*", fig.pos = "h", fig.align = "center", fig.width=7, fig.height=3, fig.cap = "Proportion of faces and hands seen as a function of age for each child in the dataset. Data are binned by each week that the videos were filmed and scaled by the number of frames in that age range. Dashed lines show estimated trend lines from proportion of faces/hands in view when detections are restricted to the center FOV, reducing the contribution of children's own hands."}

ggplot(wide_uncropped, 
       aes(x=age_day_bin, y=prop, 
           size=log10(num_frames_total),
           col=region)) +
  geom_point(alpha=.2) +
  geom_smooth(span=10, aes(weight = num_frames_total), show.legend = FALSE) + # geom_smooth(show.legend = FALSE) or move these below legend?
  geom_smooth(data = wide_center, span=10, aes(weight = num_frames_total), show.legend = FALSE, 
              lty = 2, span=10, se = FALSE) +
  ylab('Proportion Detections') + 
  xlab('Age (Months)') +
  ylim(0,.5) +
  facet_grid(.~child_id) + 
  theme_few(base_size=9) +
  ggthemes::scale_color_solarized(name = "") + 
  scale_size_continuous(name = "Detections (Log 10)") +
  theme(legend.text=element_text(size=8)) +
  theme(legend.position="bottom")

@@

We analyzed the social information in view across the entire dataset, looking specifically at the proportions of faces and hands that were in view for each child.^[All analyses and preprocessed data files for this paper are available at https://tinyurl.com/detecting-social-info] Data from videos were binned according to the age of the child (in weeks). First, we saw that the proportion of faces in view showed a moderate decrease across this age range (see Figure \ref{fig:FacesAndHands}); in contrast, we did not observe an increase in the proportion of hands in view, but rather a slight decrease. These effects were quantified with two separate linear mixed-models (see Tables 1 & 2).^[Face/hand detections were binned across each week of filming. Participant's age was converted into months and centered for these analyses. Random slopes for the effect of age by child led to a singular fit and were removed from both analyses; see full model specification in accompanying codebase.]

As children's hands tended to occur in the lower visual field (see Figure \ref{fig:handLocation}), we thus re-analyzed the entire dataset while restricting our analysis to the center field of view, decreasing the proportion of hand detections from `r round(sum(all_vid_data$num_hands)/sum(all_vid_data$num_detect),2)*100`% to `r round(sum(all_vid_data_center$num_hands)/sum(all_vid_data_center$num_frames),2)*100`%, but only decreased face detections from `r round(sum(all_vid_data$num_faces)/sum(all_vid_data$num_detect),2)*100`% to `r round(sum(all_vid_data_center$num_faces)/sum(all_vid_data_center$num_frames),3)*100`%. This cropping likely removed both the majority of detections of children's own hands but also some detections of adult hands (see Figure \ref{fig:handLocation}), especially as OpenPose was biased to miss children's hands when they were in view. Nonetheless, within this modified field of view, we still observed more hand detections than face detections (see dashed lines in Figure \ref{fig:FacesAndHands}).

```{r eval=FALSE}
summary_by_age_days_centered <- all_vid_data_center %>%
  group_by(age_days,child_id) %>%
  summarize(num_faces = sum(num_faces), num_hands = sum(num_hands), num_detect = sum(num_frames)) %>%
  mutate(prop_faces = num_faces / num_detect, prop_hands = num_hands / num_detect) 
summary_by_age_days_centered$age_scale <- scale(summary_by_age_days_centered$age_days, scale = FALSE)[,1] / 30.3

summary_by_age_days <- all_vid_data %>%
  group_by(age_days,child_id) %>%
  summarize(num_faces = sum(num_faces), num_hands = sum(num_hands), num_detect = sum(num_frames)) %>%
  mutate(prop_faces = num_faces / num_detect, prop_hands = num_hands / num_detect) 
summary_by_age_days$age_scale <- scale(summary_by_age_days$age_days, scale = FALSE)[,1] / 30.3

@@

```{r eval=FALSE}
# run lmer models -- faces over age
faces_model_full_age_out = summary(lmer(prop_faces ~ age_scale + (1 | child_id), data = summary_by_age_days_centered))

# hands over age
hands_model_full_age_out = summary(lmer(prop_hands ~ age_scale + (1 | child_id), data = summary_by_age_days_centered))

# explicit modeling of faces vs. hands and interaction with age
# main effect of ages and regions; no interaction.
wide_centered_age_days <- summary_by_age_days_centered %>%
  gather(region, prop, prop_faces, prop_hands) %>%
  mutate(approach = "cropped",
         region = ifelse(region == "prop_faces","Face","Hands"))

diff_model_full_age_out = summary(lmer(prop ~ region*age_scale + (1 | child_id), data = wide_centered_age_days))
```

```{r eval=FALSE}
xtable(faces_model_full_age_out$coefficients, digits=c(4,3,3,3,3,3),"Model coefficients from a linear mixed model predicting the proportion of faces seen by infants in the center FOV.")

xtable(hands_model_full_age_out$coefficients, digits=c(4,3,3,3,3,3),"Model coefficients from a linear mixed model predicting the proportion of hands seen by infants n the center FOV.")
```

\begin{table}[ht]
\centering
\begin{tabular}{rrrrrr}
  \hline
 & Estimate & Std. Error & df & t value & Pr($>$$|$t$|$) \\ 
  \hline
(Intercept) & 0.100 & 0.014 & 1.955 & 7.049 & 0.021 \\ 
  Age  & -0.002 & 0.001 & 386.972 & -4.461 & 0.000 \\ 
   \hline
\end{tabular}
\caption{Model coefficients from a linear mixed model predicting the proportion of faces seen by infants in the center FOV.} 
\end{table}

\begin{table}[ht]
\centering
\begin{tabular}{rrrrrr}
  \hline
 & Estimate & Std. Error & df & t value & Pr($>$$|$t$|$) \\ 
  \hline
(Intercept) & 0.166 & 0.011 & 2.082 & 15.340 & 0.004 \\ 
  Age & -0.002 & 0.001 & 380.308 & -3.114 & 0.002 \\ 
   \hline
\end{tabular}
\caption{Model coefficients from a linear mixed model predicting the proportion of hands seen by infants in the center FOV.} 
\end{table}

## Access to social information in different locations
```{r}
load(here::here('data/data_preprint/saycam_metadata.RData')) # meta

@@

```{r}
vid_data_by_location <- all_vid_data %>%
  mutate(num_frames = num_detect) %>%
  mutate(age_day_bin = cut(age_days, bins, labels=round(bin_starts/30,1))) %>%
  mutate(age_day_bin = as.numeric(as.character(age_day_bin))) %>%
  left_join(meta) %>%
  filter(!is.na(Location)) %>%
  filter(count_locations==1)

vid_data_centered_by_location <- all_vid_data_center %>%
  mutate(age_day_bin = cut(age_days, bins, labels=round(bin_starts/30,1))) %>%
  mutate(age_day_bin = as.numeric(as.character(age_day_bin))) %>%
  left_join(meta) %>%
  filter(!is.na(Location)) %>%
  filter(count_locations==1)

# 
vid_data_by_location$Location = droplevels(vid_data_by_location$Location) 
vid_data_centered_by_location$Location = droplevels(vid_data_centered_by_location$Location) # get rid of unused levels (more than 1 location)

# merge locations that seem similar
levels_to_modify = levels(vid_data_by_location$Location)
levels_to_modify = levels(vid_data_centered_by_location$Location)
levels_to_modify[10] = 'Outside' # Outside on property
levels_to_modify[12] = 'Outside' # Off Property

# reset levels for both cropped/uncropped
levels(vid_data_centered_by_location$Location) <- levels_to_modify
levels(vid_data_by_location$Location) <- levels_to_modify

@@

```{r}
face_hand_by_location_centered<- vid_data_centered_by_location %>%
  group_by(Location,child_id,age_day_bin) %>%
  summarize(prop_faces = sum(num_faces)/sum(num_frames), prop_hands = sum(num_hands)/sum(num_frames), num_detect = sum(num_frames))  %>%
  group_by(Location) %>%
  filter(num_detect >12000)

face_hand_by_location <- vid_data_by_location %>%
  group_by(Location,child_id,age_day_bin) %>%
  summarize(prop_faces = sum(num_faces)/sum(num_frames), prop_hands = sum(num_hands)/sum(num_frames), num_detect = sum(num_frames))  %>%
  group_by(Location) %>%
  filter(num_detect >12000)

## Compute CIs for faces/hands by each location, and then merge back raw data so they can be plotted together
## Get rid of any locations where we didn't have enough data to make a CI (not more than 1 age_bin)
hands_to_plot_centered <- face_hand_by_location_centered %>%
  group_by(Location, child_id) %>%
  multi_boot_standard(col="prop_hands") %>%
  mutate(region = "Hands (Center)") %>%
  ungroup %>%
  left_join(face_hand_by_location_centered) %>%
  mutate(prop = prop_hands) %>%
  select(-prop_faces, -prop_hands) %>%
  filter(!is.na(ci_lower))

faces_to_plot_centered <- face_hand_by_location_centered %>%
  group_by(Location, child_id) %>%
  multi_boot_standard(col="prop_faces") %>%
  mutate(region = "Face (Center)") %>%
  ungroup %>%
  left_join(face_hand_by_location_centered) %>%
  mutate(prop = prop_faces) %>%
  select(-prop_faces, -prop_hands) %>%
  filter(!is.na(ci_lower))  # if we didn't have enough points to make a CI, filter

faces_to_plot_all <- face_hand_by_location %>%
  group_by(Location, child_id) %>%
  multi_boot_standard(col="prop_faces") %>%
  mutate(region = "Faces (All)") %>%
  ungroup %>%
  left_join(face_hand_by_location) %>%
  mutate(prop = prop_faces) %>%
  select(-prop_faces, -prop_hands) %>%
  filter(!is.na(ci_lower))  # if we didn't have enough points to make a CI, filter

hands_to_plot_all <- face_hand_by_location %>%
  group_by(Location, child_id) %>%
  multi_boot_standard(col="prop_hands") %>%
  mutate(region = "Hands (All)") %>%
  ungroup %>%
  left_join(face_hand_by_location) %>%
  mutate(prop = prop_hands) %>%
  select(-prop_faces, -prop_hands) %>%
  filter(!is.na(ci_lower))  # if we didn't have enough points to make a CI, filter

all_to_plot <- faces_to_plot_centered %>%
  full_join(hands_to_plot_centered) %>%
  full_join(hands_to_plot_all) %>%
  full_join(faces_to_plot_all) %>%
  group_by(Location) %>%
  mutate(num_detect_location = sum(num_detect)) %>%
  ungroup() %>%
  mutate(Location = fct_reorder(Location, num_detect_location))
```

@@

```{r include=FALSE}
### Chi-squared tests for location variability
vid_data_by_location_A <- vid_data_by_location %>%
  filter(child_id == "A") %>%
  group_by(Location) %>%
  summarize(num_faces_by_loc = sum(num_faces), num_no_faces_by_loc = sum(num_detect)-num_faces_by_loc,
            num_hands_by_loc = sum(num_hands),  num_no_hands_by_loc = sum(num_detect)-num_hands_by_loc)

vid_data_by_location_S <- vid_data_by_location %>%
  filter(child_id == "S") %>%
  group_by(Location) %>%
  summarize(num_faces_by_loc = sum(num_faces), num_no_faces_by_loc = sum(num_detect)-num_faces_by_loc,
            num_hands_by_loc = sum(num_hands),  num_no_hands_by_loc = sum(num_detect)-num_hands_by_loc)
